---
title: "9041 Assignment 2"
author: Selena
date: today
format: 
    html:
      toc: true
      code-fold: true
      code-summary: "Show code"
      df-print: paged
execute:
    echo: false
    warning: false
---

```{r, load libraries}
#| output: FALSE
# Output false ensures your reproducible document does not show all of your code!

# Remember to install packages you do not already have

library(tidyverse)
library(readxl)
library(psych)
library(gt)
library(janitor)
```

```{r}
#| output: FALSE

# Load data
data<-read_excel("./Attachment_Anxiety_Data.xlsx")


# Inspect data for the big five dataset
head(data)
```

```{r, clean data}
#| output: FALSE

# Use mutate to rename variables in a meaningful way - such that those assigned gender value 1 in the dataset are listed as Male and those assigned gender value of 2 are listed as Female. Do the same for education values
# Extract for only variables age, Gender, education, and big five values
# Mutate to convert bfi values to integers

data.clean <- data |>
    mutate(Gender = case_when(Gender==1 ~ "Male", Gender==2 ~"Female", TRUE ~ "NA")) |> 
    mutate(Relationship = case_when(Relationship==1 ~ "Married", Relationship==2 ~ "In a Relationship", Relationship==4 ~ "Divorced", Relationship==5 ~ "In a Relationship", Relationship==6 ~ "Never been in a Relationship", Relationship==7 ~ "Prefer not to say",TRUE ~ "NA")) |> 
    select(Gender, Relationship, SA_1:SEst_10) |>
    mutate_at(3:41, as.integer)

```

```{r, score items}
#| output: FALSE

# Answer key: which items belong to each subscale.
# "-" marks reverse-coded items (e.g., E1 "Don't talk a lot" -> high = LESS extraverted), which get flipped so higher scores always mean more of the trait.

keys_SIAS<- list(Social_Interaction_Anxiety_Scale=c("SA_1", "SA_2", "SA_3", "SA_4", "-SA_5", "SA_6",
                                                       "SA_7", "SA_8", "-SA_9", "SA_10", "-SA_11", "SA_12",
                                                       "SA_13", "SA_14", "SA_15", "SA_16", "SA_17",
                                                       "SA_18", "SA_19", "SA_20"))
keys_ECRS<- list(Experiences_in_Close_Relationships_Scale=c("AA_1", "AA_2", "AA_3", "AA_4", "AA_5", 
                                                          "AA_6", "AA_7", "AA_8", "AA_9"))
keys_RSE<- list(Rosenberg_SelfEsteem_Scale = c("SEst_1", "-SEst_2", "SEst_3", "SEst_4", "-SEst_5", 
                                               "-SEst_6","SEst_7", "-SEst_8", "-SEst_9", "SEst_10"))


# Average items per person, and compute Cronbach's alpha.
# Returns $scores (per-person scores as averages since we set totals to F) and $alpha (reliability)
scores_SIAS<-scoreItems(keys_SIAS, data.clean, totals = F, min=0, max=4)
scores_ECRS<-scoreItems(keys_ECRS, data.clean, totals = F, min=1, max=7)
scores_RSE<-scoreItems(keys_RSE, data.clean, totals = F, min=1, max=4)


# Turn this into a dataframe!
scores_SIAS.df<-as.data.frame(scores_SIAS$scores)
scores_ECRS.df <- as.data.frame(scores_ECRS$scores)
scores_RSE.df <- as.data.frame(scores_RSE$scores)

# Combine data frame
allscores.df <- cbind(scores_SIAS.df, scores_ECRS.df, scores_RSE.df)

```

```{r, combine data frames}
#| output: FALSE

# Combine the original data set with the new scores dataframe
total.clean<-cbind(data.clean, allscores.df)

# Inspect new data set
head(total.clean)
```

```{r, reduced data}
#| output: FALSE

# Select only for the columns which you want to appear in your final data table
total.final<- total.clean |>
    select("Gender", "Relationship", "Social_Interaction_Anxiety_Scale", "Experiences_in_Close_Relationships_Scale", "Rosenberg_SelfEsteem_Scale") |>
    mutate_if(is.numeric, round, 2)
```

```{r, reproducible table for education distribution}
#| output: FALSE

# Create a demographics table of education by gender
demographictable <- total.final |>
  tabyl(Relationship, Gender)

# Create your reproducible gt table
gttable.1 <- demographictable |>
  gt() |>
  tab_header(
    title = md("*Distribution of Males and Females by Education Level*")
  )

```

```{r, reproducible table for big five scores}
#| output: FALSE

# Combine the three Cronbach's alpha values and round them to 2 decimal places.
alphas <- round(c(
  scores_SIAS$alpha,
  scores_ECRS$alpha,
  scores_RSE$alpha
), 2)

# Summary statistics for certain columns
summary <- describe(select(total.final, Social_Interaction_Anxiety_Scale:Rosenberg_SelfEsteem_Scale))
summary

# Label sample size for later in your reproducible document using describe
n <- (describe(total.final))[1,2]

# Name an object of Subscales so this can appear in your table
Scales <- c("Social_Interaction_Anxiety_Scale", "Experiences_in_Close_Relationships_Scale", "Rosenberg_SelfEsteem_Scale")

# Create a column called Subscales in your summary table
summary$Scales<- Scales


# Select for only the columns which you want to appear in your final table
summary <- summary |>
    select(Scales, mean, median, sd, range) |>
       mutate_if(is.numeric, round, 2)

# Combine summary information with alpha values
final.reptable <- cbind(summary, alphas)

# Create a reproducible table
gttable.2<- gt(final.reptable) |>
    tab_header(
        title = md("*Descriptive Statistics for the Attachment and SociaL Anxiety Scales*")) |>
    tab_stubhead(label= "Composites")|>
    tab_spanner(
        label="Central Tendency",
        columns = c(mean, median)
    )|>
        tab_spanner(
        label="Variability",
        columns = c(sd, range)
        )|>
            tab_spanner(
        label="Reliability Values (Chronbach's alpha)",
        columns = c(alphas)
            ) 

```

```{r, filtered dataset}
#| output: FALSE

# Use filter to extract only those participants who are over 18 and under 65

total.filtered <- total.clean |>
    filter(Relationship == "Married" | Relationship == "In a Relationship")

# Checking that age restriction worked
table(total.filtered$Relationship) 
```

```{r, reproducible FILTERED table for big five scores}
#| output: FALSE

# Combine the three Cronbach's alpha values and round them to 2 decimal places.
alphas_filtered <- round(c(
  scores_SIAS$alpha,
  scores_ECRS$alpha,
  scores_RSE$alpha
), 2)

# Summary statistics for certain columns
summary_filtered <- describe(select(total.filtered,Social_Interaction_Anxiety_Scale:Rosenberg_SelfEsteem_Scale ))
summary_filtered

# Name an object of Subscales so this can appear in your table
Scales <- c("Social_Interaction_Anxiety_Scale", "Experiences_in_Close_Relationships_Scale", "Rosenberg_SelfEsteem_Scale")

#Create a column called Subscales in your summary table
summary_filtered$Scales<- Scales

# Select for only the columns which you want to appear in your final table
summary_filtered <- summary_filtered |>
    select(Scales, mean, median, sd, range) |>
       mutate_if(is.numeric, round, 2)

# Combine summary information with alpha values
filtered.reptable <- cbind(summary_filtered, alphas_filtered)

# Create a reproducible table
gttable.3<- gt(filtered.reptable) |>
    tab_header(
        title = md("*Descriptive Statistics for the Attachment and Social Anxiety Scales in people Married or In a Relationship*")) |>
    tab_stubhead(label= "Composites")|>
    tab_spanner(
        label="Central Tendency",
        columns = c(mean, median)
    )|>
        tab_spanner(
        label="Variability",
        columns = c(sd, range)
        )|>
            tab_spanner(
        label="Reliability Values (Chronbach's alpha)",
        columns = c(alphas_filtered)
            ) 
```
## Intro

## Methods

### Participants

In this data set there were `{r} n` participants, with varying distributions of education type (Table 1).

`{r} gttable.1`

### Measures

In this attachment and social anxiety data set, the 3 scales refer to the .... SIAS (Cronbach's alpha = `{r} alphas[1]`). ECRS (Cronbach's alpha = `{r} alphas[2]`), RES (Cronbach's alpha = `{r} alphas[3]`). 

### Data Analysis Strategy

The data for variables xyz were reverse keyed.

## Results

`{r} gttable.2`
In this attachment and social anxiety data set, participants had a mean score on SIAS of `{r} final.reptable[1,2]`, on ECRS of `{r} final.reptable[2,2]`, on RES of `{r} final.reptable[3,2]`.

`{r} gttable.3`
When only including participants married or in a relationship, this attachment and social anxiety data set, the 3 scales refer to the 3 composites included in the scales. Participants had a mean score on SIAS of `{r} filtered.reptable[1,2]`, on ECRS of `{r} filtered.reptable[2,2]`, on RES of `{r} filtered.reptable[3,2]`.

## Discussion

